### 2015-08-07 background.tex
fix

\begin{definition}
\label{definition:datarace}
A \emph{data race} occurs when two distinct threads access a shared memory location, at least one of the accesses modifies the location, at least one of the accesses is non-atomic, and there is no mechanism in place to prevent these accesses from being simultaneous.
\end{definition}

>>>>

\begin{definition}
\label{definition:datarace}
A \emph{data race} occurs when two distinct threads access a shared memory location, at least one of the accesses is a write access, at least one of the accesses is non-atomic, and there is no mechanism in place to prevent these accesses from being simultaneous.
\end{definition}
